\LARGE \bf A Pipeline to Assemble (Near-)Collision Footage Datasets

### 2020-11-11 paper.tex

\newcommand{\todo}[1]{{\color{red}#1}}

@@

\begin{figure}[htpb]
		\centering
		% TODO: Uncomment this
    %\includegraphics[width=0.5\textwidth]{images/example_metadata.png}
		\caption{An example of metadata for a labelled video. Both automatic metadata about the source of the video and manual annotation of the collision is maintained. Each bounding box contains the object classification, a unique identifier and a boolean value representing if the tracked agent is involved in a collision.}
		\label{fig:images-example_metadata-png}
\end{figure}

\todo{Use a better image}

>>>>

\newcommand{\todo}[1]{{\color{red}#1}}
\usepackage{listings, xcolor}

\colorlet{punct}{red!60!black}
\definecolor{background}{HTML}{EEEEEE}
\definecolor{delim}{RGB}{20,105,176}
\colorlet{numb}{magenta!60!black}

\lstdefinelanguage{json}{
    basicstyle=\normalfont\ttfamily,
    numbers=left,
    numberstyle=\scriptsize,
    stepnumber=1,
    numbersep=8pt,
    showstringspaces=false,
    breaklines=true,
    frame=lines,
    backgroundcolor=\color{background},
    literate=
     *{0}{{{\color{numb}0}}}{1}
      {1}{{{\color{numb}1}}}{1}
      {2}{{{\color{numb}2}}}{1}
      {3}{{{\color{numb}3}}}{1}
      {4}{{{\color{numb}4}}}{1}
      {5}{{{\color{numb}5}}}{1}
      {6}{{{\color{numb}6}}}{1}
      {7}{{{\color{numb}7}}}{1}
      {8}{{{\color{numb}8}}}{1}
      {9}{{{\color{numb}9}}}{1}
      {:}{{{\color{punct}{:}}}}{1}
      {,}{{{\color{punct}{,}}}}{1}
      {\{}{{{\color{delim}{\{}}}}{1}
      {\}}{{{\color{delim}{\}}}}}{1}
      {[}{{{\color{delim}{[}}}}{1}
      {]}{{{\color{delim}{]}}}}{1},
}

@@

\subsection{Metadata}
After all of the previous steps have been completed, the pipeline is able to produce a metadata object.
There are many fields in the metadata object (as can be seen in Figure \ref{metadata_example}):

\begin{itemize}
  \item "collision\_type" contains the type of collision in the video (e.g. car vs. car)
  \item "description" contains a breif description of the video as scraped from the video hosting website
  \item "download\_src" contains the site that the video was sourced from (e.g. YouTube)
  \item "tags" is an object that contains custom user-defined tags on videos and additional data that is site specific
  \item "title" is a string that represents the type of the video
  \item "url" is the url that the video was fetched from
  \item "is\_split\_url" is a boolean that represents if all of the frames of the video have bounding boxes in this metadata
  \item "start\_i" is the start frame of the video that the bounding boxes are created for (if is\_split\_url is true)
  \item "end\_i" is the end frame of the video the bounding boxes are created for (if is\_split\_url is true)
  \item "bb\_fields" contains all bounding-box specific data. Each entry is a list, where the $i_{th}$ index in each contains the data for one bounding-box:
  \begin{itemize}
    \item "ids[$i$]" represents what vehicle id the $i_{th}$ bounding box represents. Each vehicle in the video has it's own unique id
    \item "cls[$i$]" represents the object class of the vehicle
    \item "frames[$i$]" represents what frame of the video the $i_{th}$ bounding box is for
    \item "has\_collision[$i$]" represents if the vehicle with id $ids[i]$ is in a collision
    \item "x1s[$i$], y1s[$i$], x2s[$i$], y2s[$i$]" are the coordinates of the two points $(x_1,y_1)$ \& $(x_2,y_2)$ that make bounding box $i$
  \end{itemize}
\end{itemize}`

\begin{figure}
  \begin{lstlisting}[language=json]
    {
      "collision_type":"",
      "description":"",
      "download_src":"",
      "tags": {
        "reddit_post_info":{
          "id":"<post_id>"
          "title":"title"
        }
      },
      "title":"Title of the Video",
      "url":"http:/www.myvideo.com",
      "is_split_url": false,
      "start_i": 0,
      "end_i": 60,
      "bb_fields": {
        "cls": [],
        "frames": [],
        "has_collision": [],
        "ids": [],
        "x1s": [],
        "y1s": [],
        "x2s": [],
        "y2s": [],
      }
    }
  \end{lstlisting}
    \caption{Example Metadata Produced by the Pipeline}
    \label{metadata_example}
\end{figure}
